\documentclass[letterpaper,12pt]{article} % Increased font size to 12pt
\usepackage{mathptmx} % Set mathptmx as the main font
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[x11names]{xcolor} % Allows fine-tuned colors
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=Blue4, % Subtle blue color; adjust as needed
    citecolor=black
}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
    \textbf{\Huge \scshape Jaid Monwar Chowdhury} \\ \vspace{1pt}
    \href{mailto:jaidmonwar.official@gmail.com}{\underline{jaidmonwar.official@gmail.com}} $|$ \small +8801781737438 $|$ \href{https://jaid-monwar.github.io}{\underline{Website}} $|$
    \href{https://github.com/jaid-monwar}{\underline{GitHub}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bangladesh University of Engineering and Technology (BUET)}{February 2020 -- March 2025}
      {Bachelor of Science in Computer Science and Engineering}{}
  \resumeSubHeadingListEnd

\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{\textbf{Chowdhury, J. M.*}, Pial, S. M. R.*, Khan, J. Y., Ratul, M. R. Z., \& Iqbal, A. (2025). \textit{Trace2Script: A Framework for Web UI Test Script Generation from Natural Language Test Cases}. \textbf{Submitted} to ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering (FSE), 2026.}
\end{itemize}


\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Prof. Reyhaneh Jabbarvand's Group, University of Illinois Urbana-Champaign}{Urbana, Illinois}
      {Remote Research Intern}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Designing a multi-language framework for automated generation of semantically meaningful unit tests across C, Java, and Python using AI agents.}
        \resumeItem{Integrated advanced testing methodologies including fuzzing (AFL++) and symbolic execution (KLEE) to enhance code coverage and cross-language parsing capabilities.}
        \resumeItem{Implemented a hybrid test oracle generation system combining static analysis with dynamic execution traces for enhanced test reliability.}
        \resumeItem{Co-authoring a paper on the framework, preparing to-be submitted at \textbf{ISSTA 2026}.}
      \resumeItemListEnd
    \resumeSubheading
      {Prof. Anindya Iqbal's Group, BUET}{Dhaka, Bangladesh}
      {Research Assistant}{March 2025 -- September 2025}
      \resumeItemListStart
        \resumeItem{Developed an automated framework leveraging LLMs to translate natural language test cases into executable Playwright test scripts for automated Web UI testing.}
        \begin{itemize}[label=$\circ$, leftmargin=0.2in]
            \item Implemented the Web Agent architecture for autonomous Web UI traversal with comprehensive trace logging of element interactions.
            \item Constructed and validated a comprehensive dataset of natural language test cases from production web applications for systematic framework evaluation.
        \end{itemize}
        \resumeItem{Developed a scalable full-stack inference system for deploying and serving locally fine-tuned LLMs.}
        \begin{itemize}[label=$\circ$, leftmargin=0.2in]
            \item Implemented automated pipelines for generating software use cases from business requirements and synthesizing corresponding test cases.
        \end{itemize}
        % \resumeItem{Co-first authored a paper soon to-be submitted at \textbf{FSE 2026}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yobo AI}{Ontario, Canada}
      {Remote Software Engineer}{June 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Developed a voice-based conversational AI agent for automating concurrent task-oriented restaurant operations (delivery, pickup, reservation, FAQs).}
        \resumeItem{Led the design of a dynamic context injection pipeline that retrieves and integrates specific knowledge into LLMs, enabling efficient querying of large-scale knowledge bases.}
        \resumeItem{Engineered the end-to-end delivery feature, including address capturing, validation using Google Maps API, and automated delivery acceptance/rejection based on distance calculation and dynamic delivery fee integration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Achievements and Awards}
\resumeSubHeadingListStart
    \resumeSubheading
      {Bangladesh Blockchain Olympiad 2024 $|$ \href{https://www.linkedin.com/posts/blockchain-olympiad-bangladesh_we-are-excited-to-announce-the-results-of-activity-7239706428721020930-wUJy?utm_source=share\&utm_medium=member_desktop}{Link}}{}
      {Honourable Mention in Both AI Category \& Blockchain Category}{September 2024}
      \resumeItemListStart
        \resumeItem{Led team to Honourable Mention among 250+ teams by developing an AI-powered health ecosystem featuring machine learning medical diagnosis and empathic AI therapist.}
        \resumeItem{Designed MEDIBLOC, a blockchain-based medical prescription management system with Attribute-Based Access Control (ABAC) for secure sharing of prescriptions between hospitals, pharmacies, and patients.}
      \resumeItemListEnd
    \resumeSubheading
      {Hello Yobo AI Hackathon 2024 $|$ \href{https://github.com/jaid-monwar/BUET_Multithreading-Athene-Companion-Yobo-AI-Hackathon.git}{Link}}{}
      {Second Runners up}{May 2024}
      \resumeItemListStart
        \resumeItem{Led team to 2nd runners-up position among 50+ teams by developing Athene, an offline Android LLM chatbot using Mediapipe API with 600 tokens/sec inference speed on mobile CPUs.}
      \resumeItemListEnd
    \resumeSubheading
      {Therap Javafest 2023 $|$ \href{https://www.linkedin.com/posts/jaid-monwar_therapbd-therapjavafest2023-codingcompetition-activity-7249066504095211520-rKat?utm_source=share\&utm_medium=member_desktop}{Link}}{}
      {Top 10 Finalist}{August 2023}
      \resumeItemListStart
        \resumeItem{Led team to Grand Finale (top 10/150+ teams) by developing a fullstack customer management application using Spring Boot and Angular with AI-powered analytics for revenue tracking and forecasting.}
      \resumeItemListEnd
    \resumeSubheading
      {SUST Technovent 2023 $|$ \href{https://www.facebook.com/share/KfyeD4yTKikFhv3z/}{Link}}{}
      {First Runners up}{January 2023}
      \resumeItemListStart
        \resumeItem{Led team to 2nd runners-up position among 170+ teams by developing a blockchain-based authentication system with RFID technology for vault security. Custom JavaScript blockchain implementation passed 69 test cases.}
      \resumeItemListEnd
    \resumeSubheading
      {HackNSU Season 3}{}
      {Second Runners up}{November 2021}
      \resumeItemListStart
        \resumeItem{Led team to 2nd runners-up position among 30+ teams by developing Remedi, a telemedicine platform with AI-powered symptom diagnosis chatbot using Intelligent Machines API.}
      \resumeItemListEnd
    \resumeSubheading
      {Academic Olympiads $|$ \href{https://www.rokomari.com/book/210061/physics-olympiad-problem-solution-compilation}{Link}}{}
      {Physics, Chemistry, Mathematics}{2017 -- 2020}
      \resumeItemListStart
        \resumeItem{Mathematics: First place winner at Jahangirnagar University Maths Olympiad.}
        \resumeItem{Physics: Translated official Olympiad book (Categories A \& B) from Bangla to English; National Round participant (2017-2019).}
        \resumeItem{Chemistry: Achieved 11th place in National Round competition.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

% \section{Activities}
% \resumeSubHeadingListStart
%     \resumeSubheading
%       {Director of Technology, BUET Cyber-Security Club}{2023 -- 2024}
%       {Bangladesh University of Engineering and Technology}{}
%       \resumeItemListStart
%         \resumeItem{Organized workshops on various cyber-security topics and arranged Capture-the-Flag (CTF) competitions.}
%       \resumeItemListEnd
%     \resumeSubheading
%       {Student Mentor}{2019 -- 2024}
%       {Bangladesh University of Engineering and Technology}{}
%       \resumeItemListStart
%         \resumeItem{Mentored several undergraduate students in research and university projects.}
%         \resumeItem{Mentored around 20 high school students in informatics, physics and mathematical olympiads.}
%       \resumeItemListEnd
% \resumeSubHeadingListEnd

\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{English:}  IELTS 8.0 (Reading: 8.5, Listening: 8.5, Speaking: 8.0, Writing: 7.5)\\
    \textbf{Bengali:} Native Proficiency
\end{itemize}

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \color[HTML]{1C033C}\textbf{Programming Languages:} Python, Java, C/C++, TypeScript, JavaScript, SQL, Shell Scripting\\
    \color[HTML]{1C033C}\textbf{Web Development:} React, Flask, FastAPI, Django, Spring Boot, HTML, CSS\\
    \color[HTML]{1C033C}\textbf{AI/ML \& Data:} PyTorch, LangChain, LangGraph, Autogen, CrewAI, PostgreSQL, SQLite, Supabase\\
    \color[HTML]{1C033C}\textbf{DevOps \& Cloud:} Docker, Linux, DigitalOcean\\
    \color[HTML]{1C033C}\textbf{Tools \& Technologies:} Git, GitHub, NodeJS, Selenium, AFL++, KLEE, Logstash, Hyperledger Fabric
\end{itemize}
\section{Reference}
\resumeSubHeadingListStart
    \resumeSubheading
        {Reyhaneh Jabbarvand}{University of Illinois Urbana-Champaign, Urbana, Illinois}
        {Assistant Professor, Computer Science and Engineering}{reyhaneh@illinois.edu}
    \resumeSubheading
        {Anindya Iqbal}{Bangladesh University of Engineering and Technology}
        {Professor, Computer Science and Engineering}{anindya@cse.buet.ac.bd}
    % \resumeSubheading
    %     {Sukarna Barua}{Bangladesh University of Engineering and Technology}
    %     {Associate Professor, Computer Science and Engineering}{sukarnabarua@cse.buet.ac.bd}
\resumeSubHeadingListEnd
\end{document}
